---
title: "INFO 370A HW 1: Review of Prerequisite Knowledge"
output: html_notebook
---

Name: *TODO*

This is a R Notebook. 
Execute this chunk by clicking the *Run* button within the chunk or by placing your cursor inside it and pressing *Cmd+Shift+Enter*. 
```{r}
plot(cars)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file).

Read more about it in Chapter 12 of the [INFO 201 textbook](https://info201.github.io/)

### 1) Write 3 things from the INFO 201 textbook that were confusing:
1.1) *TODO*

1.2) *TODO*

1.3) *TODO*


### Vectors
```{r}
# Set variable vec_even to a vector of even numbers from 2 to 100 (inclusive). 
vec_even <- #TODO

# Set variable vec_odd to a vector of odd numbers from 1 to 99 (inclusive).
vec_odd <- #TODO

# Set variable vec_sum to the sum of vec_even and vec_odd.
vec_sum <- #TODO

# Work on 2.1 below
  
```

How many values in vec_sum are greater than the mean?

2.1) *TODO*: Write a function get_upper which takes in a vector of numbers and returns the number of values which are greater than the mean. So get_upper(c(1,3,2,5)) would return 2.

2.2) *TODO*: How many values in vec_sum are greater than the mean?

### Importing libraries
Now we're just importing some libraries. If you get errors when you run this, you may need to install some packages (see Ch 10.2).
```{r}
library(MASS) # access to Boston data frame
data(mtcars) # data on motor trend car road tests

library(dplyr) # data wrangling package. See Chapter 10 in INFO 201 textbook
library(ggplot2) # plotting library. See Chapter 13 of INFO 201 textbook
```



### Learning about Vehicle Efficiancy
We will now play with some data from 1974 Motor Trend Car Road Tests. The data exists in a dataframe _mtcars_.
```{r}
?mtcars # learn more about the dataframe
View(mtcars) # see the dataframe
  
# Show work for 3.1-3.4 here!

```
What is the mean horsepower for all cars?
3.1) *TODO*

What is the mean horsepower for cars with 4 cylinders?
3.2) *TODO*

What is the mean fuel efficiency (in MPG) for cars with a displacement between 100 and 200 cu. in.?
3.3) *TODO*

3.4) *TODO*: Use ggplot to plot the relationship between vehicle displacement (x-axis) and miles per gallon (y-axis)


Our friends in Europe now want to see this data but they want it converted to metric!
```{r}
#conversion ratios
MPG_KML_RATIO <- 0.35400619 # 1 Miles/Gallon = 0.35 Kilometer/Liter
CIN_L_RATIO <- 0.0163871 # 1 cubic inch = 0.016 Liter

# Add a column "kml" to the mtcars dataframe which provides the kilometers / liter for each car. The conversion from MPG to KML is provided by MPG_KML_RATIO.
mtcars$kml <- #TODO
  
# Add a column "disp_l" to the mtcars dataframe which provides the displacement for each car in liters. The conversion from cubic inches to liters is provided by CIN_L_RATIO.
mtcars$disp_l <- #TODO

# Convert mtcars$cyl to a factor (see Chapter 9.3)
mtcars$cyl <- #TODO

# Show 4.1 and 4.2 below!

```

4.1) *TODO* Use ggplot to plot the relationship between vehicle displacement in liters and kilometers/liter. Color the points by number of cylinder. Give the plot a title, label both axes.

Based on your plot in 4.1, comment on the relationship between displacement, fuel efficiency, and cylinders. 
4.2) *TODO*

### Looking at Boston housing data
```{r}
# Work on 5.1-5.3 below

?Boston # getting more information on the dataset

boston <- Boston
View(boston) # Viewing data


```
What does a row in the Boston dataset represent?
5.1) *TODO* 

What is the median value of owner-occupied homes for the 5 neighborhoods with the highest per capita crime rate that tract bound the Charles River? (hint: see Chapter 10)
5.2) *TODO*

What is the median value of owner-occupied homes for the 5 neighborhoods with the highest per capita crime rate that do NOT tract bound the Charles River?
5.3) *TODO*


Last question: How long did this assignment take you?
6.1) *TODO*

That's it for this assignment. Great job!
